Preliminary results on trion signature in time-resolved ARPES

### 2023-11-28 preliminary-summary.tex
update derivation of trion Hamiltonian

In the case of two-dimensional materials, $\vb{k}_\parallel = \vb{k}'$.
Within the framework of the two-band model, 
it has been shown~\cite{rustagi2018photoemission} that 
the signature of an exciton has the dispersion relation of
\begin{equation}
    \omega = E_{S \vb{Q}} + \epsilon_{v \vb{k}_\parallel - \vb{Q}},
\end{equation}
where $E_{S \vb{Q}}$ is the single exciton energy, 
i.e. band gap plus the negative binding energy.
In the case of a positive trion, 
there is no single, definite dispersion relation that determines the shape of the ARPES signature;
assuming that after one electron is driven out, 
scatterings between the two remaining holes are negligible, 
the dispersion of the trion ARPES signature is determined by the following family of curves 
\begin{equation}
    \omega = E_{S \vb{P}} + \epsilon_{v \vb{k}_{\text{h1}}} + \epsilon_{v \vb{k}_{\text{h2}}}, \quad 
    \vb{k}_\parallel - \vb{k}_{\text{h1}} - \vb{k}_{\text{h2}} = \vb{P}.
\end{equation}
In \prettyref{fig:arpes-exciton-trion}, it could be observed that 
in the zero-temperature case,
even when a trion mode and an exciton mode with the same energy,
they still result in different ARPES signatures:
the slopes and curvatures of the ARPES signature are different, 
and when the total momentum of the excitation is given, 
the position shifts of the signature on the ARPES heatmap are also different.

\begin{figure}
    \centering
    \includegraphics[width=0.9\textwidth]{images/exciton-trion-comparison.pdf}
    \caption{Comparison between exciton signatures and trion signatures.}
    \label{fig:arpes-exciton-trion}
\end{figure}

>>>>

In the case of two-dimensional materials, $\vb{k}_\parallel = \vb{k}'$.
Within the framework of the two-band model, 
it has been shown~\cite{rustagi2018photoemission} that 
the signature of an exciton has the dispersion relation of
\begin{equation}
    \omega = E_{S \vb{Q}} + \epsilon_{v \vb{k}_\parallel - \vb{Q}},
\end{equation}
where $E_{S \vb{Q}}$ is the single exciton energy, 
i.e. band gap plus the negative binding energy, 
and $\epsilon_{v \vb{k}} < 0$ is the valence band energy from the Fermi energy.
In the case of a positive trion, 
there is no single, definite dispersion relation that determines the shape of the ARPES signature;
assuming that after one electron is driven out, 
scatterings between the two remaining holes are negligible, 
the dispersion of the trion ARPES signature is determined by the following family of curves 
\begin{equation}
    \omega = E_{S \vb{P}} + \epsilon_{v \vb{k}_{\text{h1}}} + \epsilon_{v \vb{k}_{\text{h2}}}, \quad 
    \vb{k}_\parallel - \vb{k}_{\text{h1}} - \vb{k}_{\text{h2}} = \vb{P}.
\end{equation}
In \prettyref{fig:arpes-exciton-trion}, it could be observed that 
in the zero-temperature case,
even when a trion mode and an exciton mode with the same energy,
they still result in different ARPES signatures:
the slopes and curvatures of the ARPES signature are different, 
and when the total momentum of the excitation is given, 
the position shifts of the signature on the ARPES heatmap are also different.

\begin{figure}
    \centering
    \includegraphics[width=0.9\textwidth]{images/exciton-trion-comparison.pdf}
    \caption{Comparison between exciton signatures and trion signatures. 
    (a), (b) Exciton ARPES signatures at $Q_x = \text{\SI{0}{\angstrom} and \SI{0.5}{\angstrom}}$.
    (c), (d) Exciton ARPES signatures at $Q_x = \text{\SI{0}{\angstrom} and \SI{0.5}{\angstrom}}$. 
    The binding energy of the trion mode is manually shifted to
    the exciton binding energy in \cite{rustagi2018photoemission}, 
    but significant differences can still be spotted 
    between exciton and trion signatures.}
    \label{fig:arpes-exciton-trion}
\end{figure}
